They are Very Smart: Genetic-Algorithm-Based Pathfinding in Games

### 2018-12-04 paper.tex
Paper: musings on what is to come

>>>>

One approach to solving this problem could be moving towards more complicated
models of selection and reproduction than our current keep \(n\) percent,
asexually reproduce the best genomes and then do a straight pass of mutation.
Moving to a system where reproductive resources are distributed according to the
Z-score (standard deviations from the mean) or similar of fitness that give more
reproductive power to individual that more drastically improve on the status quo
could allow for a system that reacts more strongly to change. Another option
could be coding part of the mutation rate in genomes to allow evolution to
determine it's own speed. The two previous approaches could even be combined for
as dynamic an evolution environment as possible.

Sexual (genderless) reproduction could also be introduced as a way of trying to
increase diversity. Plain sexual reproduction without any further restrictions
could allow good traits that evolve in parallel to be combined into a single
individual with the benefits of both, which has fairly obvious advantages.
This simple approach to sexual reproduction could, however, force a single
species to dominate quickly depending on how well neural net parameters combine,
as it could easily be the case that two disparately evolving neural nets combine
into a total dud, despite having fit parents. One way around that would be to
condition reproduction on similarity, such genomes are more likely to reproduce
with those that are structurally similar. Another approach would be to allow
genomes to determine mating preference based on other genomes' content and
fitness, and then run them through a tournament to determine mates. This would
have the additional benefit of allowing additional emergent behavior that has
not been conceived of in this speculation.

Conceptually, evolving neural nets has the massive benefit of not worrying about
how to differentiate and nicely back-propagate

individuals that jump out ahead of the population could

Discussion: talk about the lack of direction vectors being fed into the neural nets.
